\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Mayur Dave}


\def\footerlink{mdave16.github.io/cv/}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, statistics, mathematics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in, 8.5in},
	left=1.0in,
	top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\renewcommand*\rmdefault{phv}

% Don't indent paragraphs.
\setlength\parindent{0em}


\begin{document}
	
	% Place name at left
	{\huge \name}
	
	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}
	\vspace{0.25in}
	

	\section*{Education}
	
	\begin{itemize}
		\item MMath from University of Warwick (2013 -- Present), Integrated Masters, predicted 2:1
		
		\item A levels from Leicester Grammar School (2011 -- 2013)
		\begin{itemize}
			\item Mathematics: A*
			\item Further Mathematics:  A*
			\item Physics:  A
			\item STEP I:  1
		\end{itemize}
	\end{itemize}
	
	
	\section*{Projects}
	
	I am a quick learner, being able to pick up new languages typically within a fortnight. I've worked on quite a few projects as coursework as well as for research purposes. Although the vast majority of work listed is mathematical, I am adaptable and can code for any purpose. Below is a short list of previous projects I've taken part in:
	
	\begin{itemize}
		\item 4th year essay on \textbf{Holomorphic Dynamics} supervised by Assistant Professor \textbf{Adam Epstein} (in Sage). Performing calculations to show that a conjecture will hold.
		
		\item Undergraduate Research Support Scheme \textbf{Computation of Bianchi Modular Forms} supervised by Research Fellow \textbf{Marc Masdeu} (in Sage). Using research papers to implement a working algorithm for the computation.
		
		\item \textbf{Project Leader} for Technology Volunteers. Preparing work sheets for children to learn coding from. Including explaining concepts to university students, teachers and parents. (in C++ and Scratch)
	\end{itemize}

	Proficient in mathematically oriented languages(Sage, Magma, Pari \dots). Adept with generic programming languages (Python, C/C++, Java). Mostly working with C and Python.
	
	\section*{Personal}
	\begin{itemize}
		\item British National with full driving licence.
		\item English, Gujarati and Hindi as native languages
		
	\end{itemize}
	\section*{Other Information}
	\begin{itemize}
		\item University of Warwick Duke of Edinburgh Society:
		\begin{itemize}
			\item Post Gold Officer (2015 -- Present)
		\end{itemize}
		 
	\end{itemize}
	% Footer
	\bigskip
	\begin{center}
		\begin{footnotesize}
			Last updated: \today \\
			\href{\footerlink}{\texttt{\footerlink}}
		\end{footnotesize}
	\end{center}

\end{document}
