\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Mayur Dave}


\def\footerlink{mdave16.github.io/cv/}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, statistics, mathematics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in, 8.5in},
	left=1.0in,
	top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\renewcommand*\rmdefault{phv}

% Don't indent paragraphs.
\setlength\parindent{0em}


\begin{document}
	
	% Place name at left
	{\huge \name}
	
	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}
	\vspace{0.25in}
	

	\section*{Education}
	
	\begin{itemize}
		\item MMath from University of Warwick (2013 -- Present), Integrated Masters, predicted 2:1
		
		\item A levels from Leicester Grammar School (2011 -- 2013)
		\begin{itemize}
			\item Mathematics: A*
			\item Further Mathematics:  A*
			\item Physics:  A
			\item STEP I:  1
		\end{itemize}
	\end{itemize}
	
	\section*{Personal Statement}
	I am a cheerful experienced teacher, having taught both in classrooms and one on one. I can learn very quickly on the job, reacting to my audience, making sure nobody is left behind when covering the basics. Having taught a large volume of students from a wide range of skill levels, I would be able to help even the most able minded students.
	
	During my time at LGS, I was slowly introduced to classroom teaching. Towards the end, I was teaching the classroom entirely on my own, including planning and marking.
	
	Similarly, while working with Technology Volunteers, I was taking on the entire class as a volunteer.
	My role expanded to Project Leader after a while of ongoing good work, which meant I was then leading lessons for teachers, university students, parents and children.
	Often also liaising with event organisers, to make sure nothing went awry.
	
	\section*{Work Experience}
	
	\begin{itemize}
		\item Technology Volunteers.
		\begin{itemize}
			\item \textbf{Volunteer} Teaching children from work sheets and answering any questions they pose not on the sheets. (Jul 15 – Jul 16)
			\item \textbf{Project Leader} Preparing above work sheets for children to learn coding from. Including explaining concepts to university students, teachers and parents. (Jul 16 – Present)
		\end{itemize}
	
		\item \textbf{Online Tutor} with MyTutor.co.uk. Consistently working on 5 star rating. (Nov 13 – Jul 15)
		
		\item \textbf{Teaching Assistant} at Leicester Grammar School, for year 8s and year 10s. (Jun 12 – May 13)
		
		\item \textbf{Private Tutor} at St Pauls RC School. Tutoring several students one to one (Feb 09 – Jun 11)
	\end{itemize}
	
	\section*{Personal}
	\begin{itemize}
		\item British National with full driving licence.
		\item English, Gujarati and Hindi as native languages
		
	\end{itemize}
	\section*{Other Information}
	\begin{itemize}
		\item University of Warwick Duke of Edinburgh Society:
		\begin{itemize}
			\item Post Gold Officer (2015 -- Present)
		\end{itemize}
		
	\end{itemize}
	% Footer
	\bigskip
	\begin{center}
		\begin{footnotesize}
			Last updated: \today \\
			\href{\footerlink}{\texttt{\footerlink}}
		\end{footnotesize}
	\end{center}

\end{document}
